healthcare access

### 2017-03-08 paper/index.Rmd
updated paper, and index.html

>>>>

```{r hi2015, echo=FALSE}
barplot(h, names.arg = m, xlab = "Healthcare Coverage for 2015", 
        ylab="Percentage (%)", col='blue', main = "Percentage of the Respondents that Has Healthcare Coverage")
```

```{r hi2015employer, echo=FALSE}
barplot(h2, names.arg = m2, xlab = "Healthcare Coverage for 2015", 
        ylab="Percentage (%)", col='blue', main = "Percentage of the Respondents that Has Healthcare Coverage")
```
